Reasoning About a Machine with Local Capabilities

### 2018-05-11 toplas/paper.tex
removed obsolete sections

As explained in \sectionname~\ref{sec:stack-and-return-pointer}, the
macro-instruction \texttt{\footnotesize{reqglob $r_1$}} checks that the callback
is global, essentially to make sure it is not allocated on the stack where it
might contain old stack pointers or return pointers. Otherwise, the
encapsulation of our local stack frame could be broken. In the proof of
Lemma~\ref{lem:correctness-g1}, this requirement shows up because we invoke the
callback in a world that is only a private future world of the one where we
received the callback, precisely because we have invalidated the adversary's
local state (particularly their old stack and return capabilities). The callback
is still valid in this private future world, but only because we know that it is
global.

\itoplassug{Suggestion: Add an actual proof sketch}
In Lemma~\ref{lem:correctness-g1} the order of control has been
inverted compared to the previous lemmas. In this lemma, the adversary
assumes control first with a capability for the closure creator
\texttt{\footnotesize{g1}}. Consequently, we need to check that all
arguments are safe to use and that we clean up before returning in the
end. The inversion of control poses an interesting challenge when it
comes to reasoning about the adversary's local state during the
execution of \texttt{\footnotesize{f4}} and the callbacks where the
adversary should not rely on the local state from before the call of
\texttt{\footnotesize{f4}}. This is easily done by revoking all the
temporary regions of the world given at the start of
\texttt{\footnotesize{f4}}. However, when \texttt{\footnotesize{f4}}
returns, the adversary is again allowed to rely on its old local state
so we need to guarantee that the local state is unchanged. This is
important because the return pointer that \texttt{\footnotesize{f4}}
receives may be local, and the adversary is allowed
to allocate the activation record on the stack (just like we do) so
they can store and recover their old stack pointer after
\texttt{\footnotesize{f4}} returns.

\begin{toplas}
In \figurename~\ref{fig:worlds-in-pf-g1}, we illustrate how we accommodate this in
the proof of Lemma~\ref{lem:correctness-g1} by constructing appropriate worlds
for all the situations where control is passed to the adversary. The potentially
local return pointer received by \texttt{\footnotesize{f4}} from the adversary
is safe in $W_1$, so it can only be used in public future worlds. Let us see how
$W_6$ is constructed as a public future world of $W_1$, as well as a private
future world of $W_5$. The worlds $W_2$ and $W_4$ are constructed by revoking
all temporary regions and adding a $\iota^\pwl$ region for the stack we pass
away and static temporary regions (a region that accepts exactly one memory) for
our local stack as well as the adversary's local stack. The given worlds $W_3$
and $W_5$ are public future worlds in which the adversary chooses to return to
us. None of these worlds can have masked the temporary regions of $W_1$ with
permanent regions. $W_6$ is constructed by revoking the temporary regions of
$W_5$ and reinstating the temporary regions of $W_1$. This makes $W_6$ a public
future world of $W_1$. It is therefore safe to use the return pointer to return
to the adversary, since we have restored validity of any local state they might
have stashed away.
\end{toplas}

>>>>

  The complete proof can be found in the technical appendix~\citep{technical_appendix}.
\end{toplas}
% As explained in \sectionname~\ref{sec:stack-and-return-pointer}, the
% macro-instruction \texttt{\footnotesize{reqglob $r_1$}} checks that the callback
% is global, essentially to make sure it is not allocated on the stack where it
% might contain old stack pointers or return pointers. Otherwise, the
% encapsulation of our local stack frame could be broken. In the proof of
% Lemma~\ref{lem:correctness-g1}, this requirement shows up because we invoke the
% callback in a world that is only a private future world of the one where we
% received the callback, precisely because we have invalidated the adversary's
% local state (particularly their old stack and return capabilities). The callback
% is still valid in this private future world, but only because we know that it is
% global.

% \itoplassug{Suggestion: Add an actual proof sketch}
% In Lemma~\ref{lem:correctness-g1} the order of control has been
% inverted compared to the previous lemmas. In this lemma, the adversary
% assumes control first with a capability for the closure creator
% \texttt{\footnotesize{g1}}. Consequently, we need to check that all
% arguments are safe to use and that we clean up before returning in the
% end. The inversion of control poses an interesting challenge when it
% comes to reasoning about the adversary's local state during the
% execution of \texttt{\footnotesize{f4}} and the callbacks where the
% adversary should not rely on the local state from before the call of
% \texttt{\footnotesize{f4}}. This is easily done by revoking all the
% temporary regions of the world given at the start of
% \texttt{\footnotesize{f4}}. However, when \texttt{\footnotesize{f4}}
% returns, the adversary is again allowed to rely on its old local state
% so we need to guarantee that the local state is unchanged. This is
% important because the return pointer that \texttt{\footnotesize{f4}}
% receives may be local, and the adversary is allowed
% to allocate the activation record on the stack (just like we do) so
% they can store and recover their old stack pointer after
% \texttt{\footnotesize{f4}} returns.

% \begin{toplas}
% In \figurename~\ref{fig:worlds-in-pf-g1}, we illustrate how we accommodate this in
% the proof of Lemma~\ref{lem:correctness-g1} by constructing appropriate worlds
% for all the situations where control is passed to the adversary. The potentially
% local return pointer received by \texttt{\footnotesize{f4}} from the adversary
% is safe in $W_1$, so it can only be used in public future worlds. Let us see how
% $W_6$ is constructed as a public future world of $W_1$, as well as a private
% future world of $W_5$. The worlds $W_2$ and $W_4$ are constructed by revoking
% all temporary regions and adding a $\iota^\pwl$ region for the stack we pass
% away and static temporary regions (a region that accepts exactly one memory) for
% our local stack as well as the adversary's local stack. The given worlds $W_3$
% and $W_5$ are public future worlds in which the adversary chooses to return to
% us. None of these worlds can have masked the temporary regions of $W_1$ with
% permanent regions. $W_6$ is constructed by revoking the temporary regions of
% $W_5$ and reinstating the temporary regions of $W_1$. This makes $W_6$ a public
% future world of $W_1$. It is therefore safe to use the return pointer to return
% to the adversary, since we have restored validity of any local state they might
% have stashed away.
% \end{toplas}
